Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings

### 2021-02-03 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Added details to schemes, added slides on MSME background

\documentclass[hideothersubsections, usenames,dvipsnames,10pt]{beamer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsmath}
\usepackage{mathpazo}
\usepackage{hyperref}
\usepackage{multimedia}
\usepackage{multicol}
\usepackage{epsfig}
\usepackage{curves}
\usepackage{epsfig}
\usepackage{epic}
\usepackage{curves}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{multicol}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{fix-cm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{natbib}

@@

% Font
\usefonttheme{serif}
\setbeamercovered{invisible}

@@

% Font
\setbeamerfont{section in sidebar}{size=\fontsize{5.3}{5}\selectfont}
\setbeamerfont{subsection in sidebar}{size=\fontsize{4.4}{5.5}\selectfont}
%\setbeamerfont{subsubsection in sidebar}{size=\fontsize{4}{7}\selectfont}
\setbeamerfont{title in sidebar}{}
\setbeamerfont{author in sidebar}{}
\setbeamercolor{section in sidebar}{bg=bdf,fg=offwhite}
\setbeamercolor{subsection in sidebar}{bg=bdf,fg=offwhite}

%\setbeamercolor{title}{bg=red!25!blue,fg=white}
%\setbeamercolor{fo} {bg=red!25!blue,fg=white}
%\setbeamercolor{sidebar}{bg=red!25!blue,fg=white}
%\setbeamercolor{author in sidebar}{fg=black!20!white}
%\setbeamercolor{title in sidebar}{fg=white}
%\setbeamercolor{normal text}{bg=white}
%\setbeamercolor{frametitle}{fg=white}
%\setbeamercolor{section in sidebar}{bg=black,fg=white}
%\setbeamercolor{subsection in sidebar}{bg=black,fg=white}
%\setbeamercolor{block title}{bg=red!25!blue,fg=white}
%\setbeamercolor{block body}{bg=blue!20!white,fg=black}
%\setbeamerfont{subsection in sidebar}{size=\tiny}
%\setbeamerfont{title in sidebar}{size=\scriptsize}
%\setbeamerfont{author in sidebar}{size=\tiny}
%\setbeamercovered{transparent}

@@

\section{\textbf{PART I: Lecture} \\ \quad \emph{Business Practices}}

@@

\begin{frame}
\frametitle{History and Prevalence}
	\begin{itemize_3pt}
		\item At least \textcolor{bdf}{USD 1 billion per year} (to 4-5 million beneficiary entrepreneurs; \citet{McKenzie2020})
		\item Classical training programs \emph{precede} evidence that business practices vary and are predictive for productivity
		\vspace{0.1in}
		\item Examples:
		\begin{itemize_3pt}
			\item Start and Improve Your Business (ILO)
			\item Business Edge (IFC)
			\item EMPRETEC Entrepreneurship Training Workshop (UNCTAD)
		\end{itemize_3pt} 
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Questions}
	\begin{itemize_3pt}
	\item Any questions?
	\vspace{0.1in}
	\item[] .. before we move on to our paper?
	\end{itemize_3pt}
\end{frame}

@@

\institute[]{
\inst{1} Tilburg University\\
\bigskip
\inst{2} UC Berkeley, CEGA\\
\bigskip
\inst{3} The World Bank}

@@

\begin{frame}
\frametitle{Background}
	\begin{itemize_3pt}
	\item Micro \& Small firms (MSEs) main \textcolor{bdf}{source of employment} in the developing world
	\vspace{0.1in}
	\item In \textcolor{bdf}{Indonesia}, MSEs represent 99\% of all firms and 94.5\% of employment 
	\vspace{0.1in}
	\item Understanding the factors fostering efficiency and growth of MSEs is an important research and policy goal
	\end{itemize_3pt}
\end{frame}

@@

\subsection{Our Approach}
\begin{frame}
\frametitle{Harnessing Cross-Firm Heterogeneity}
\begin{itemize_3pt}
\item Some facts about business practices in firms:
	\begin{itemize_3pt}	
	\item Vast heterogeneity in business practices and performance across similar businesses (de Mel, McKenzie \& Woodruff, 2009)
	\item Variation in practices accounts for more than 20\% of variation in productivity within the same firm in the US (Bloom et al, 2019)
	\end{itemize_3pt}
\vspace{0.1in}
\pause
\item Research thus far has mostly overlooked this underlying heterogeneity in design and implementation of programs
\vspace{0.1in}
\pause
\item Our idea is to make it \textcolor{bdf}{central} to the research design: 
	\begin{itemize_3pt}
	\item Use variation across businesses to identify business practices associated with successful performance
	\item Instead of teaching set courses, provide consulting, or matching; we curate what works from local peers
	\item Test different communication channels and their cost-effectiveness
\end{itemize_3pt}
\end{itemize_3pt}

@@

\subsection{Discussion}
\begin{frame}
\frametitle{Efficiency Gains?}
\begin{enumerate_3pt}
\item Unpacking impacts on practices shows improvements in efficiency practices:
\vspace{0.1in}
\begin{itemize_3pt}
\item Adjust stocks based on product profitability
\item Negotiate lower prices with suppliers
\item Consult with former customers
\item Offer discounts
\item Make joint decisions
\item Review financial performance to identify channels of improvement
\item Make anticipated budget for upcoming costs
\end{itemize_3pt}
\vspace{0.1in}
\pause
\item These are non-record-keeping practices. Also, variance in profits among the treated businesses does not converge
\vspace{0.1in}
\pause
\item Causal-mediation analysis shows that the most important drivers of impact on sales and profits are stocking up and marketing practices.
\end{enumerate_3pt}
\vspace{0.1in}
$\rightarrow$ \textcolor{bdf}{Efficiency gains}
\end{frame}

@@

\subsection{References}
\begin{frame}[allowframebreaks]
\frametitle{References}

>>>>

\documentclass[hideothersubsections, usenames,dvipsnames,11pt]{beamer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsmath}
\usepackage{mathpazo}
\usepackage{hyperref}
\usepackage{multimedia}
\usepackage{multicol}
\usepackage{epsfig}
\usepackage{curves}
\usepackage{epsfig}
\usepackage{epic}
\usepackage{curves}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{multicol}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{fix-cm}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{natbib}

@@

@@

% Font
\usefonttheme{serif}
\setbeamercovered{invisible}
\setbeamerfont{section in sidebar}{size=\fontsize{5.3}{5}\selectfont}
\setbeamerfont{subsection in sidebar}{size=\fontsize{4.4}{5.5}\selectfont}
%\setbeamerfont{subsubsection in sidebar}{size=\fontsize{4}{7}\selectfont}
\setbeamerfont{title in sidebar}{}
\setbeamerfont{author in sidebar}{}
\setbeamercolor{section in sidebar}{bg=bdf,fg=offwhite}
\setbeamercolor{subsection in sidebar}{bg=bdf,fg=offwhite}
\linespread{1.25}

%\setbeamercolor{title}{bg=red!25!blue,fg=white}
%\setbeamercolor{fo} {bg=red!25!blue,fg=white}
%\setbeamercolor{sidebar}{bg=red!25!blue,fg=white}
%\setbeamercolor{author in sidebar}{fg=black!20!white}
%\setbeamercolor{title in sidebar}{fg=white}
%\setbeamercolor{normal text}{bg=white}
%\setbeamercolor{frametitle}{fg=white}
%\setbeamercolor{section in sidebar}{bg=black,fg=white}
%\setbeamercolor{subsection in sidebar}{bg=black,fg=white}
%\setbeamercolor{block title}{bg=red!25!blue,fg=white}
%\setbeamercolor{block body}{bg=blue!20!white,fg=black}
%\setbeamerfont{subsection in sidebar}{size=\tiny}
%\setbeamerfont{title in sidebar}{size=\scriptsize}
%\setbeamerfont{author in sidebar}{size=\tiny}
%\setbeamercovered{transparent}
\setbeamerfont{itemize/enumerate body}{size={\fontsize{9.5}{9.5}}}
\setbeamerfont{itemize/enumerate subbody}{size={\fontsize{8}{8}}}
%\setbeamerfont{itemize/enumerate subbody}{family=\sffamily}

@@

\section{\textbf{PART I: Lecture} \\ \quad \emph{Business Practices and Training}}

@@

\begin{frame}
\frametitle{History and Prevalence}
	\begin{itemize_3pt}
		\item At least \textcolor{bdf}{USD 1 billion per year} (to 4-5 million beneficiary entrepreneurs; \citet{McKenzie2020})
		\item Classical training programs \emph{precede} evidence that business practices vary and are predictive for productivity
		\item Examples:
		\begin{itemize_3pt}
			\item Start and Improve Your Business (ILO)
			\item Business Edge (IFC)
			\item EMPRETEC Entrepreneurship Training Workshop (UNCTAD)
		\end{itemize_3pt} 
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Questions}
	\textcolor{bdf}{Any questions?}
	\begin{itemize_3pt}
	\item[] .. before we move on to our paper?
	\end{itemize_3pt}
\end{frame}

@@

\institute[]{
\inst{1} Tilburg University \\
\inst{2} UC Berkeley, CEGA\\
\inst{3} The World Bank}

@@

\begin{frame}
\frametitle{Background}
	\begin{itemize_3pt}
	\item Micro and small firms (MSEs) are typically the main \textcolor{bdf}{source of employment} in the developing world
	\item In \textcolor{bdf}{Indonesia}, MSEs represent .. 
	\begin{itemize_3pt}
		\item .. 99\% of all firms
		\item .. 94.5\% of employment
	\end{itemize_3pt} 
	\item Understanding the factors fostering efficiency and growth of MSEs is an important research and policy goal
	\end{itemize_3pt}
\end{frame}

@@

\subsection{Our Approach}
\begin{frame}
\frametitle{Harnessing Cross-Firm Heterogeneity}
Some stylized facts about business practices in small firms
\begin{itemize_3pt}
	\item Vast heterogeneity in business practices and performance across similar businesses \citep{deMel2009}
	\item Variation in practices accounts for more than 20\% of variation in productivity within the same firm in the US \citep{Bloom2019}
	\item[] $\rightarrow$ Research has largely overlooked this heterogeneity in program design and implementation
\end{itemize_3pt}

\vspace{0.5em}
\pause

Our idea is to \textcolor{bdf}{make productice use of this heterogeneity} in research design: 
\begin{itemize_3pt}
	\item Use cross-firm variation to identify \textcolor{bdf}{practices associated with business performance}
	\item \textcolor{bdf}{Curate local best practices}
	\item Test different \textcolor{bdf}{modes of delivery}, and their cost-effectiveness
\end{itemize_3pt}

@@

\subsection{Discussion}
\begin{frame}
\frametitle{Efficiency Gains?}
Unpacking impacts on business practices $\rightarrow$ \textcolor{bdf}{efficiency practices}:
\vspace{0.1in}
\begin{itemize_3pt}
	\item Adjust stocks based on product profitability
	\item Negotiate lower prices with suppliers
	\item Consult with former customers
	\item Offer discounts
	\item Make joint decisions
	\item Review performance to identify ways to improve
	\item Make anticipated budget for upcoming costs
	\vspace{0.1in}

	\pause

	\item[] $\rightarrow$ \textcolor{bdf}{Non-record-keeping practices}
	\vspace{0.1in}

	\pause

	\item[] $\rightarrow$ Causal-mediation analysis: \textcolor{bdf}{Stocking up and marketing practices} drive performance effects

	\pause

	\item[] $\rightarrow$ Variance in profits among treated firms does not converge

	\item[] $\rightarrow$ \textcolor{bdf}{Efficiency gains}
\end{itemize_3pt}
\end{frame}

@@

%\section*{\textbf{APPENDIX}}

%\subsection{References}
\begin{frame}[allowframebreaks]
\frametitle{References}
